Demes: a specification for interchanging complex demography

### 2022-04-05 paper.tex
uncommented IM figure

%\begin{figure}[h!]
%    \begin{minipage}{0.44\textwidth}
%        \begin{tcolorbox}
%            \inputminted[fontsize=\scriptsize,linenos,numbersep=5pt]{yaml}{models/IM.yaml}
%        \end{tcolorbox}
%        \begin{tcolorbox}
%            \includegraphics[width=\textwidth]{fig/IM}
%        \end{tcolorbox}
%    \end{minipage}\hfill
%    \begin{minipage}{0.54\textwidth}
%        \begin{tcolorbox}
%            \inputminted[fontsize=\scriptsize,linenos,numbersep=5pt]{yaml}{models/IM-resolved.yaml}
%        \end{tcolorbox}
%    \end{minipage}\\
%    \caption{
%        \label{fig:IM}
%        Example isolation-with-migration Demes model. (A) The compact non-redundant
%        representation expressed using YAML. (B) The same model in the fully-qualified
%        form. (C) A visual representation of the model using \texttt{demesdraw}.
%        The YAML descriptions in (A) and (B) correspond exactly to a JSON description,
%        but are much more human-readable.
%    }
%\end{figure}

>>>>

\begin{figure}[h!]
    \begin{minipage}{0.44\textwidth}
        \begin{tcolorbox}
            \inputminted[fontsize=\scriptsize,linenos,numbersep=5pt]{yaml}{models/IM.yaml}
        \end{tcolorbox}
        \begin{tcolorbox}
            \includegraphics[width=\textwidth]{fig/IM}
        \end{tcolorbox}
    \end{minipage}\hfill
    \begin{minipage}{0.54\textwidth}
        \begin{tcolorbox}
            \inputminted[fontsize=\scriptsize,linenos,numbersep=5pt]{yaml}{models/IM-resolved.yaml}
        \end{tcolorbox}
    \end{minipage}\\
    \caption{
        \label{fig:IM}
        Example isolation-with-migration Demes model. (A) The compact non-redundant
        representation expressed using YAML. (B) The same model in the fully-qualified
        form. (C) A visual representation of the model using \texttt{demesdraw}.
        The YAML descriptions in (A) and (B) correspond exactly to a JSON description,
        but are much more human-readable.
    }
\end{figure}
